---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mathutils

<!-- badges: start -->
<!-- badges: end -->

Mathematical and Statistical Utility Functions for R

## Overview

The **mathutils** package provides a collection of utility functions for common mathematical and statistical operations. It includes functions for data normalization, enhanced statistical summaries.

## Key Features

- **Enhanced Statistical Summary**: Comprehensive statistics including measures of central tendency, variability, and distribution shape

## Installation

You can install the development version of mathutils from [GitHub](https://github.com/) with:

``` r
devtools::install_github("sayali-bot/mathutils")
```


## Functions Overview

mathutils provides four main utility functions:

| Function | Purpose |
|----------|---------|
| `enhanced_summary()` | Comprehensive statistical summary |
| `normalize_data()` | Data normalization (min-max or z-score) |
| `percent_change()` | Calculate percentage changes |
| `detect_outliers()` | Identify outliers using IQR method |

## Usage Examples



## Development

This package was developed following modern R package development practices using:

- **usethis**: Package setup and maintenance automation
- **devtools**: Development, testing, and installation tools
- **roxygen2**: Documentation generation from inline comments
- **testthat**: Unit testing framework

## License

This project is licensed under the MIT License - see the LICENSE file for details.

## Contact

- Author: Sayali Salunkhe
- Email: salunkhesayali20@gmail.com
- GitHub: [@sayali-bot](https://github.com/sayali-bot)

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(mathutils)
## basic example code
```
